\section{Conclusion}
\label{sec:conclusion}

We asked when a hand-crafted array-geometry prior helps SELD, using a controlled
one-bit ablation across modality and three temporal backbones. The effect on
direction is \textbf{graded by temporal inductive bias}: recurrent cells shift
non-positively, Transformer cells positively, and the Conformer occupies a
near-neutral middle position rather than a second harmful extreme. The most
robust effect is the FOA recurrent benefit, which replicates zero-shot on
STARSS22 at full significance; the strongest harm is the MIC Transformer
contrast. A factorial ANOVA confirms the recurrent-versus-Transformer
architecture$\times$prior interaction, and a controlled probe shows that the
effect is behavioural rather than a shift in linearly decodable direction.
Orthogonally, the architecture that governs direction is inert on distance---a
dissociation, not two crossed interactions. A second injection mechanism,
\texttt{convbias}, does not strengthen this claim into a mechanism-invariant
law; instead it exposes rerun, checkpoint-selection, and injection-site
sensitivity, thereby bounding the primary GCA result. The practical conclusion
is therefore conditional rather than universal: explicit geometry priors are
useful design choices only in the context of a particular backbone and injection
path, and should be ablated rather than assumed. We release a reproducible
multi-seed pipeline so future work can audit other priors, injection sites, and
backbones with the same protocol.
